---
title: "Assignment 2 Question1"
author: "Anurag"
date: "2022-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1
```{r}

library(tinytex)
library(kableExtra)
```



Suppose X denote the number of goals scored by home team in premier league. We can assume X is a
random variable. Then we have to build the probability distribution to model the probability of number
of goals. Since X takes value in N = {0, 1, 2, · · · }, we can consider the geometric progression sequence as
possible candidate model, i.e
$$
S =\left \{ a,ar^2,ar^3,\cdot \cdot \cdot \cdot \cdot  \right \}
$$
But we have to be careful and put proper conditions in place and modify S in such a way so that it becomes
proper probability distributions\br

1) Figure out the necesary conditions and define the probability distribution model using S.\br


```{r}
x=c(0,1,2,3)
Probability=c("a","ar","ar^2","ar^3")
Distribution_table=data.frame(x,Probability)

```

```{r}
kable(Distribution_table,"pipe",align=c("r","r"),table.attr = "class=\"striped\"")

```
under the consideration $\\\left | r \right |<=1$

$$
\sum_{k=0}^{}(ar^k)=1\\
\frac{a}{1-r}=1\\
a=1-r\\
a+r=1\\
$$

2)Check if mean and variance exists for the probability model\br

To check the existance of $E(X)$:(By Usiing Dalemberts Ratio test)


$$
E(x)=\sum_{k=0}^{inf}k(ar^k)\\
\lim_{n->inf}\frac{(n+1))ar^(n+1)}{(n)ar^n}\\
=\ r*\lim_{n->inf}(1+\frac{1}{n})\\
\
=\ r
$$


We already know that $\\\left | r \right |<=1$ .Thus through
D alemberts ratio test for infinite series we can say that $E(X)$ exists

To check the existance of $E(X^2)$:(By Usiing Dalemberts Ratio test)

$$
E(x^2)=\sum_{k=0}^{inf}k^2(ar^k)\\
\lim_{n->inf}\frac{(n+1)^2ar^(n+1)}{(n)^2ar^n}\\
=\ r*\lim_{n->inf}(1+\frac{1}{n^2})\\
\
=\ r
$$
We already know that $\\\left | r \right |<=1$ .Thus through
D alemberts ratio test for infinite series we can say that $E(X)$ exists

To check the existance of $E(X^2)$:(By Usiing Dalemberts Ratio test)

$$
E(x^2)=\sum_{k=0}^{inf}k^2(ar^k)\\
\lim_{n->inf}\frac{(n+1)^2ar^(n+1)}{(n)^2ar^n}\\
=\ r*\lim_{n->inf}(1+\frac{1}{n^2})\\
\
=\ r
$$
$E(X^2)$:\br

$$
E(x^2)=\sum_{k=0}^{inf}k^2(ar^k)\\
=\ ar+4(ar^2)+9(ar^3)+\cdot \cdot \cdot \cdot\\
=\ ar(1+r)(1-r)^-3
$$

$V(X)=E(X^2)-(E(X))^2$ 

$$
V(X)=ar(1+r)^-3-a^2r^2(1-r)^-4
$$
4)From historical data we found the following summary statistics\br
Using the summary statistics and your newly defined probability distribution model find the following:
 a. What is the probability that home team will score at least one goal?\br

 b. What is the probability that home team will score at least one goal but less than four goal?
 
We have three equations
$$
\\V(X)=9/4\\
\\E(X)=3/2\\
\\a+r=1\\
$$
From the three equations we compute the value of a=2/5 and r=3/5

Probability that the team will score atleast one goal

```{r}
geom=function(a,r,n){
  ans=0
  for (i in 0:n){
    ans=ans+a*(r)^i
  }
  return (ans)
}
```


```{r}
1-geom(2/5,3/5,0)
```


Probability that the team will score atleast one goal but less than 4 goals

```{r}
geom(2/5,3/5,3)-geom(2/5,3/5,0)
```
5. Suppose on another thought you want to model it with off-the shelf Poisson probability models. Under the assumption that underlying distribution is Poisson probability find the above probabilities, i.e.,
 a. What is the probability that home team will score at least one goal?
 b. What is the probability that home team will score at least one goal but less than four goal?
 
```{r}
pois=function(lambda,n){
  
  ans=0
  for (i in 0:n){
    ans=ans+((exp(-lambda))*(lambda)^i)/factorial(i)
  }
  return (ans)
}
```
 
```{r}
1-pois(3/2,0)
```
```{r}
pois(3/2,3)-pois(3/2,0)
```
6. Which probability model you would prefer over another?

I would prefer the geometric model over the poisson model because n ie the no of goals scored cannot be infinitely large and as calculated the r is not indefinitely small.


7.Write down the likelihood functions of your newly defined probability models and Poisson models. Clearly mention all the assumptions that you are making.

geometric model

$$
L_1(x)=\prod_{i=0}^{n}f(x_i)\\
\ = a^nr^{\sum_{i=1}^{n}x_i}
$$

Poisson model
$$
L_2(x)=\prod_{i=0}^{n}f(x_i)\\
\ =e^(-n\lambda)\frac{\lambda^(\sum_{i=1}^{n}x_i)}{\prod_{i=1}^{n}x_i}
$$

Assumptions:
1) random variable $x_1$,$x-2$,..... are iid's \
2) $\\\left | r \right |<=1$ \


