---
title: "Question4"
author: "Pawan Kumar"
date: '2022-11-16'
output:
  pdf_document:
    latex_engine: xelatex
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Problem 4**

### *Part -A: We want to predict the Claims as function of Holders. So we want to fit the following models:*
                
Claims $i=β^0 + β^1$ $Holders_{i} + ε_{i}$ , $i = 1,2,··· ,n$
Assume : $ε_{i}$ ∼ N(0,$σ^{2}$ ). Note that $β^{0} ,β^{1}$ ∈ R and $σ\in R^{+}$.

The above model can alse be re-expressed as,
                       $Claims_{i} ∼ N(µ_{i},σ^{2} )$, where
                       $µ_{i} = β^{0} + β^{1} Holders_{i} + ε_{i}$ , $i = 1,2,··· ,n$

(i) Clearly write down the negative-log-likelihood function in R. Then use optim function to estimate MLE of $θ = (β^{0} ,β^{1} ,σ)$
(ii) Calculate Bayesian Information Criterion (BIC) for the model.

```{r}

library(SciViews)
library(MASS)
H=Insurance$Holders
C=Insurance$Claims

k=length(H)
Loglikelihood <- function(pars,y)
{
  lf= 0
  for(i in 1:k)
  {
    lf=lf+dnorm(y[,1][i],mean = pars[1]+(pars[2]*y[,2][i]),sd=exp(pars[3]),log = TRUE)
  }
  return(-lf)
}

d = optim(c(0,1,50),Loglikelihood,y=data.frame(cbind(C,H)))
d
BIC=ln(k)*(length(d$par))+2*d$value 
BIC
plot(C~H)
abline(d$par[1],d$par[2],col='green')

```

### *Part -B: Now we want to fit the same model with change in distribution:*

                  
Claims $i=β^0+β^1  Holders_{i} + ε^{i}$ , $i = 1,2,··· ,n$
Assume : $ε_{i} ∼ Laplace(0,σ^2)$. Note that $β^0 , β^1 \in R$ and $σ \in R^{+ }$.
(i) Clearly write down the negative-log-likelihood function in R. Then use optim function to estimate MLE of θ = (β 0 ,β 1 ,σ)
(ii) Calculate Bayesian Information Criterion (BIC) for the model.


```{r}
rm(list=ls())
library(MASS)
plot(Insurance$Holders,Insurance$Claims
     ,xlab =
       'Holders'
     ,ylab=
       'Claims'
     ,pch=
       20
)
grid()
attach(Insurance)
data=Insurance
data=data.frame(cbind(Claims,Holders))



library(SciViews)
library(jmuOutlier)
library(MASS)
H=Insurance$Holders
C=Insurance$Claims

Loglaplace <- function(theta,data){
  lf=0
  n=nrow(data)
  for(i in 1:n){
    lf=lf+log(dlaplace(data[,1][i]-theta[1]-theta[2]*data[,2][i],0,(theta[3])))
    
  }
  return(-lf)
}

b2=optim(c(9,0.1,50),Loglaplace,data=data)
b2
n=nrow(data)
BIC2=log(n)*(3)-2*(-1*b2$value)
BIC2
plot(log(Insurance$Claims)~log(Insurance$Holders))
abline(b2$par[1],b2$par[2],col='red')

```

### *Part - C: We want to fit the following models*

$Claims_{i} ∼ LogNormal(µ_{i},σ^{2} )$,where
$µ_{i} = β^{0} + β^{1} log(Holders_{i} )$, $i = 1,2,...,n$
Note that $β^{0} ,β^{1} \in R$ and $σ \in R^{+}$ .

```{r}
library(SciViews)
library(jmuOutlier)
library(MASS)


data=data.frame(cbind(Insurance$Claims,Insurance$Holders))
data = data[-61,]
n=length(Insurance$Holders)-1

LogNormal=function(pars,data)
{
  lf=0
  for(i in 1:n)
  {
    lf=lf+log(dlnorm(data[,1][i] , pars[1]+pars[2]*log(data[,2][i]), pars[3]))
  }
  return(-lf)
}



d3=optim(c(1,0,1),LogNormal,data=data)
d3
BIC3=ln(n)*(length(d3$par))-2*ln(d3$value)
BIC3

plot(log(Insurance$Claims)~log(Insurance$Holders))
abline(d3$par[1],d3$par[2],col= 'blue')

```

### *Part - D: We want to fit the following models:*

$Claims_{i} ∼ Gamma(α_{i} ,σ)$,where
$log(α_{i} ) = β_{0} + β_{1} log(Holders_{i} )$, $i = 1,2,...,n$
(iii) Compare the BIC of all three models

```{r}
library(SciViews)
library(jmuOutlier)
library(MASS)

data=data.frame(cbind(Insurance$Claims,Insurance$Holders))
data = data[-61,]
n=length(Holders)-1

LogGamma=function(pars,data)
{
  lf=0
  for(i in 1:n)
  {
    lf=lf+log(dgamma(data[,1][i] , exp(pars[1]+pars[2]*log(data[,2][i])), scale = pars[3]))
    
  }
  return(-lf)
}


d4=optim(c(-3,0.11,1),LogGamma,data=data)
d4
BIC4=ln(n)*(length(d4$par))-2*ln(d4$value)
BIC4
plot(log(Insurance$Claims)~log(Insurance$Holders))
abline(d4$par[1],d4$par[2],col="violet")


```

