---
title: "Question_2"
author: "Pawan Kumar"
date: '2022-11-15'
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## **Problem 2**

### *Q.1. Write a function in R which will compute the MLE of θ = log(α) using* 
    *optim function in R. You can name it MyMLE*



MyMLE <- function(pars,y){
  alpha <- pars[1]
  sigma <- pars[2]
  logl <- sum(-log(gamma(alpha))-alpha*log(sigma)+(alpha-1)*log(y)-y/sigma)
  return(-logl)
}
optim(pars,MyMLE,y)



### *Q.2 Choose n=20, and alpha=1.5 and sigma=2.2*

1. *(i).  Simulate {X1 ,X2 ,··· ,Xn } from  rgamma(n=20,shape=1.5,scale=2.2)*
1. *(ii). Apply the MyMLE to estimate θ and append the value in a vector*
1. *(iii) Repeat the step (i) and (ii) 1000 times*
1. *(iv) Draw histogram of the estimated MLEs of θ.*
1. *(v) Draw a vertical line using abline function at the true value of θ*
1. *(vi) Check if the gap between 2.5 and 97.5-percentile points are shrinking* 
   *as sample size n is increasing?*

```{r}
rgamma(n=20,shape=1.5,scale=2.2)  #simulation of data for particular given 
#values of respective parameters


MyMLE <- function(pars,y){
  alpha <- pars[1]
  sigma <- pars[2]
  logl <- sum(-log(gamma(alpha))-alpha*log(sigma)+(alpha-1)*log(y)-y/sigma)
  return(-logl)
}
optim(c(1.5,2.2),MyMLE,y = rgamma(n=20,shape=1.5,scale=2.2)) #MyMLE function


ne<- function(x){
  MyMLE <- function(pars,y){
    alpha <- pars[1]
    sigma <- pars[2]
    logl <- sum(-log(gamma(alpha))-alpha*log(sigma)+(alpha-1)*log(y)-y/sigma)
    return(-logl)
  }
  optim(c(1.5,2.2),MyMLE,y = rgamma(n=20,shape=1.5,scale=2.2))
}


n <- 1000
#give 1 to function new n times
dat <- lapply(rep(1,n),ne)
#replicate 1000 times
#re1000 <- replicate(n, ne(1), simplify=FALSE)
#head(re1000)
#making a dummy function 
lap <- lapply(seq_len(n), function(x) ne(1))
head(lap)

v <- c()
for(i in 1:1000){
  v <- append(v,dat[[i]][[1]][1])
}                                 #repetation of MyMLE 1000 times and 
#appending vector for corresponding value of theta

head(v)    #pulling few data

hist(v)    #plotting histogram

abline(v = 1.5,col='blue') # for drawing vertical line using abline function


quant = quantile(v, probs = c(2.5/100,97.5/100))
diff = quant[2]-quant[1]
paste('2.5 percentile point is', quant[1])
paste("97.5 percentile point is ", quant[2])
paste(" The gap between 2.5 and 97.5-percentile for n=20, and alpha=1.5 and sigma=2.2 is ",diff)

```


### *Q.3 Choose n=40, and alpha=1.5 and repeat the (2).*

```{r}
rgamma(n=40,shape=1.5,scale=2.2)  #simulation of data for particular given 
#values ofrespective parameters

MyMLE <- function(pars,y){
  alpha <- pars[1]
  sigma <- pars[2]
  logl <- sum(-log(gamma(alpha))-alpha*log(sigma)+(alpha-1)*log(y)-y/sigma)
  return(-logl)
}
optim(c(1.5,2.2),MyMLE,y = rgamma(n=40,shape=1.5,scale=2.2)) #MyMLE function for 
#particular given values of respective parameters


ne<- function(x){
  MyMLE <- function(pars,y){
    alpha <- pars[1]
    sigma <- pars[2]
    logl <- sum(-log(gamma(alpha))-alpha*log(sigma)+(alpha-1)*log(y)-y/sigma)
    return(-logl)
  }
  optim(c(1.5,2.2),MyMLE,y = rgamma(n=40,shape=1.5,scale=2.2))
}


n <- 1000
#give 1 to function new n times
dat <- lapply(rep(1,n),ne)
#replicate 1000 times
#replicate(n, ne(1), simplify=FALSE)
#making a dummy function 
lap1 <- lapply(seq_len(n), function(x) ne(1))
head(lap1)


v <- c()
for(i in 1:1000){
  v <- append(v,dat[[i]][[1]][1])
}                           #repetation of MyMLE 1000 times and 
#appending vector for corresponding value of theta.     


head(v) #pulling few data

hist(v)  #plotting histogram



abline(v = 1.5,col='blue')   # for drawing vertical line using abline function



quant = quantile(v, probs = c(2.5/100,97.5/100))
diff = quant[2]-quant[1]
paste('2.5 percentile point is', quant[1])
paste("97.5 percentile point is ", quant[2])
paste(" The gap between 2.5 and 97.5-percentile for n=40, and alpha=1.5 and 
      sigma=2.2 is ",diff)

```


### *Q.4 Choose n=100, and alpha=1.5 and repeat the (2).*

```{r}
rgamma(n=100,shape=1.5,scale=2.2)#simulation of data for particular given values 
#of respective parameters

MyMLE <- function(pars,y){
  alpha <- pars[1]
  sigma <- pars[2]
  logl <- sum(-log(gamma(alpha))-alpha*log(sigma)+(alpha-1)*log(y)-y/sigma)
  return(-logl)
}
optim(c(1.5,2.2),MyMLE,y = rgamma(n=100,shape=1.5,scale=2.2))  # MyMLE function 
#for particular given values of parameters




ne<- function(x){
  MyMLE <- function(pars,y){
    alpha <- pars[1]
    sigma <- pars[2]
    logl <- sum(-log(gamma(alpha))-alpha*log(sigma)+(alpha-1)*log(y)-y/sigma)
    return(-logl)
  }
  optim(c(1.5,2.2),MyMLE,y = rgamma(n=100,shape=1.5,scale=2.2))
}


n <- 1000
#give 1 to function new n times
dat <- lapply(rep(1,n),ne)
#replicate 1000 times
#replicate(n, ne(1), simplify=FALSE)
#making a dummy function 
lap2 <- lapply(seq_len(n), function(x) ne(1))
head(lap2)


v <- c()
for(i in 1:1000){
  v <- append(v,dat[[i]][[1]][1])
}                                  #repetation of MyMLE 1000 times and 
#appending vector for corresponding value of theta.      


head(v) #pulling only few data

hist(v)  #plotting histogram



abline(v = 1.5,col='blue')  #drawing vertical line using abline function



quant = quantile(v, probs = c(2.5/100,97.5/100))
diff = quant[2]-quant[1]
paste('2.5 percentile point is', quant[1])
paste("97.5 percentile point is ", quant[2])
paste(" The gap between 2.5 and 97.5-percentile for n=100, and alpha=1.5 and sigma=2.2 is ",diff)

```


### *Q.5  Check if the gap between 2.5 and 97.5-percentile points are shrinking*
*as sample size n is increasing?*

* For n =20, the gap is approx. ~2.2154
  for n = 40, the gap is approx. ~1.2814
  for n = 100, the gap is approx. ~0.8006
  it turns out the gap between 2.5 and 97.5 percentile points is shrinking as 
  the sample size increases.
